---
title: "Exercice2"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r }
library(readxl)
library(dplyr)
library(tidygraph)
library(tidyverse)
library(ggraph)

DATASET_EX2 <- read_excel("C:/Users/Mehdi/Desktop/2022-ona-assignements/EX2/DATASET_EX2.xlsx")
df = DATASET_EX2
df

```

## Including Plots

You can also embed plots, for example:

```{r }

my_graph = as_tbl_graph(df)

ggraph(my_graph) + 
  geom_edge_link() + 
  geom_node_point()+
  geom_node_text(aes(label = name)) +
  theme_graph()

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Centrality degree

```{r }

centrality_deg = my_graph %>% activate(nodes) %>% mutate(degree_of_centrality = centrality_degree())

centrality_deg

```

## Betweeness degree

```{r }

betweeness = centrality_deg %>% activate(nodes) %>% mutate(betweenness = centrality_betweenness())

betweeness
  



```
``` {r }

betweeness %>% filter(name %in% c('A','B','C','D'))

```

# Conclusion

Regarding the centrality degree, it clearly comes that B,C and D are the most interesting seats. They all have the same centrality degree, equal to 5, while A is at 3. The betweeness score allows to select the seat B within the seats B,C,D because it's the one with the highest betweeness score. To note that the seat A is the one with the highest betweeness but considering that it's for a short period of time that the person will be taking the bus, it's more important to build a network rather than being the person that allows to connect people or groups. However, if it's for a long period, the seat A could be interesting as it will act like a bridge to connect two distant groups.

To sum up, if it's for short period, seat B is the more indicated. If it's for a long period, seat A is more important. 



``` {r }

ggraph(betweeness,  "stress", bbox = 15) +
  geom_edge_link2(aes(edge_colour = "Red"), edge_width = 1) +
  geom_node_point(aes(fill = betweenness, size = degree_of_centrality), shape = 22) +
  geom_node_text(aes(label = name), family = "serif") + geom_node_text(aes(label = degree_of_centrality), repel = TRUE) +
  scale_size(range = c(2, 5), guide = "none") +
  theme_graph() 



```


